Equalizer 2.0 --\\Convergence of a Parallel Rendering Framework

### 2018-08-12 paperIEEE.tex
Really final touches
git-svn-id: https://dev.ifi.uzh.ch/vmml/svn/Equalizer16@145 db7c848b-7755-4df2-b763-8796797afa52

\begin{IEEEbiography}[{
\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{images/stefan}}]{
Stefan Eilemann} works towards large-scale visualization for Exascale
simulations; interactive integration of simulation, analysis and visualization
as well as flexible frameworks for data sharing and dynamic allocation of
heterogenous resources. He was the technical manager of the Visualization Team
in the Blue Brain Project, is the CEO and founder of Eyescale, and the lead
developer of the \textsf{Equalizer} parallel rendering framework. He received
his masters degree in Computer Science from EPFL in 2015, and his Engineering
Diploma in Computer Science in 1998. He is currently working towards a PhD in
Computer Science at the Visualization and MultiMedia Lab at the University of
Zurich. \end{IEEEbiography}

>>>>

\begin{IEEEbiography}[{
\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{images/stefan}}]{
Stefan Eilemann} works on large data visualization and parallel rendering. He
was the technical manager of the Visualization Team in the Blue Brain Project,
is the CEO and founder of Eyescale, and the lead developer of the
\textsf{Equalizer} parallel rendering framework. He received his masters degree
in Computer Science from EPFL in 2015, and an Engineering Diploma in Computer
Science in 1998. He is working towards a PhD in Computer Science at the
Visualization and MultiMedia Lab at the University of Zurich.
\end{IEEEbiography}
